---
title: "models"
output: html_document
---


```{r setup, include=FALSE}

if(!require("pacman")) install.packages("pacman"); library(pacman)
p_load("tidyverse", "here", "readr", "lattice", "hexbin", "stargazer", "lme4", 
          "gridExtra", "stringr", "Hmisc","psych", "scales", "workflowr",
          "readxl", "vioplot", "expss", "jtools", "broom", "kableExtra", "knitr",
          "sjlabelled", "naniar", "summarytools", "GGally", "correlation", "dplyr", "janitor", "ggplot2", 'rio','survey', 'parsedate','sjPlot', 'sjmisc', "scales", "reshape2", "skimr", "kableExtra","testthat", "patchwork", "tidyr", "utils", "tidybayes", "ggalt", "ggstance", "ISLR", "rstanarm", "brms", "standardize", "mctest", "car", "pls", "corrplot", "corrgram", "wesanderson", "huxtable", "arm", "fastDummies")


source(here('code/functions.R'))

knitr.table.format = "html"
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

```


```{r load and filter data, include=FALSE, echo=FALSE}
dat_path_1 <-
  here("data/tracking_survey_w1_public.csv")
data_1 <- read.csv(dat_path_1) %>%
  filter(consent == 5) %>%
  filter(Finished == 1) %>%
  filter(age > 17) %>%
  filter(attention_check == 1) %>%
  rename (id = X,
          reduce_lik_mild = participant_benefit)
colnames(data_1)
dim(data_1)

dat_path_2 <-
  here("data/tracking_survey_w2_public.csv")
data_2 <- read.csv(dat_path_2) %>%
  filter(consent == 5) %>%
  filter(Finished == 1) %>%
  filter(age > 17) %>%
  filter(attention_check == 1 | att_check_bt == 1) %>%
  rename (id = X)
colnames(data_2)
dim(data_2)

dat_path_3 <-
  here("data/tracking_survey_w3_public.csv")
data_3 <- read.csv(dat_path_3) %>%
  filter(consent == 5) %>%
  filter(Finished == 1) %>%
  filter(age > 17) %>%
  filter(attention_check == 1) %>%
  rename (id = X)
colnames(data_3)
dim(data_3)

dat_path_4 <-
  here("data/tracking_survey_w4_public.csv")
data_4 <- read.csv(dat_path_4) %>%
  filter(consent == 5) %>%
  filter(Finished == 1) %>%
  filter(age > 17) %>%
  filter(attention_check == 1) %>%
  rename (id = X)
colnames(data_4)
dim(data_4)



```


## Regression models


Wave 3 - prepare variables

```{r, wave 3 covariates}

mod3_data <- data_3 %>% dplyr::select(
  c(
    contains("wv"),
    contains("Conspir"),
    trust_intentions_bt,
    trust_respectpriv_bt,
    data_security_bt,
    starts_with('sci'),
    starts_with('acc_general_'),
    COVID_sev_general,
    COVID_pers_harm,
    COVID_pers_concern,
    COVID_concern4others,
    age,
    education,
    gender,
    COVID_govresponse_3,
    Gov_helpful,
    RKI_download,
    risk_of_harm_bt,
    proportionality_bt,
    data_security_bt,
    reduce_lik_bt,
    return_activ_fut,
    reduce_spread_fut,
    COVID_info_source_6,
    COVID_info_trust_6,
    COVID_info_source_2,
    COVID_info_trust_2
  )
) %>%
  dplyr::filter(gender<3) %>%
  drop_na


acceptability <-
  mod3_data %>% dplyr::select(starts_with('acc_general_'))
Acceptability <-
  revscore(acceptability, 4) %>% apply(., 1, mean, trim = .2, na.rm = TRUE)  


Libertarianism <-
  mod3_data %>% dplyr::select(c(wv_freemarket_best, wv_freemarket_lim, wv_lim_gov)) %>% mutate(wv_freemarket_lim_rev = revscore(wv_freemarket_lim, 7)) %>%
  dplyr::select(-wv_freemarket_lim) %>% apply(., 1, mean, na.rm = TRUE)  


COVIDrisk <-
  mod3_data %>% dplyr::select(c(
    COVID_sev_general,
    COVID_pers_harm,
    COVID_pers_concern,
    COVID_concern4others
  )) %>% apply(., 1, mean, na.rm = TRUE)  
# 1 - sehr schwach

Govguidelines_helpful <-
  mod3_data %>% dplyr::select(Gov_helpful) %>% apply(., 1, mean, na.rm = TRUE)  
# 1 = Gar nicht hilfreich

COVID_govresponse =  revscore(mod3_data$COVID_govresponse_3, 5) # 1 = extrem gut (reverse to 1 = gar nicht gut)
Germany_handling_thepandemic <- COVID_govresponse



Conspiracism <- mod3_data %>% dplyr::select(contains("Conspir")) %>%
  mutate(Conspir_4 = revscore(Conspir_4_REV, 5)) %>%
  dplyr::select(-Conspir_4_REV) %>%
  apply(., 1, mean, na.rm = TRUE)  


# 1 = Falsch

Scitech_positive <- mod3_data  %>% dplyr::select(starts_with('sci')) %>%
  apply(., 1, mean, na.rm = TRUE)  
# 1 - stimme nicht zu


Education_recode = dplyr::recode(
  mod3_data$education,
  `4` = "low",
  `1` = "low",
  `2` = "low",
  `3` = "medium",
  `5` = "high",
  .default = NULL
)
Education <- factor(Education_recode, ordered = TRUE, levels = c("low", "medium", "high")) 


RKI_download = dplyr::recode(
  mod3_data$RKI_download,
  `1` = 1,
  `2` = 0,
  .default = NULL
)
CWA_download <- RKI_download


Trust_appsecurity <-
  mod3_data %>% dplyr::select(starts_with("trust"),  data_security_bt) %>% apply(., 1, mean, na.rm =
                                                                            TRUE)  

CWA_effectiveness <-
  mod3_data %>% dplyr::select(reduce_lik_bt, return_activ_fut, reduce_spread_fut) %>% apply(., 1, mean, na.rm =
                                                                                       TRUE)  

Risk_of_harm <- mod3_data$risk_of_harm_bt



Gender_recode_male = dplyr::recode(
  mod3_data$gender,
  `1` = 1,
  `2` = 0,
  `3` = 0,
  .default = NULL
)
Gender_male <- Gender_recode_male

Age <- mod3_data$age

Socialmedia_source_and_trust <-
  mod3_data %>% dplyr::select(COVID_info_source_2, COVID_info_trust_2) %>% apply(., 1, mean, na.rm =
                                                                            TRUE)  

Govannouncements_source_and_trust <-
  mod3_data %>% dplyr::select(COVID_info_source_6, COVID_info_trust_6) %>% apply(., 1, mean, na.rm =
                                                                            TRUE)  


model_data3 <-
     as.data.frame(cbind(
      CWA_download,
      Acceptability,
      Libertarianism,
      Conspiracism,
      Scitech_positive,
      COVIDrisk,
      Govguidelines_helpful,
      Trust_appsecurity,
      Risk_of_harm,
      Education,
           Age,
      CWA_effectiveness,
      Germany_handling_thepandemic,
      Socialmedia_source_and_trust,
      Govannouncements_source_and_trust,
      Gender_male
    ) ) %>% mutate(Education = factor(Education, ordered = FALSE,  levels = c(2, 1, 3), labels = c("medium", "low", "high")) )

contrasts(model_data3$Education) <- contr.treatment(levels(model_data3$Education))




```


Wave 4 - prepare variables

```{r, wave 4 covariates}


mod4_data <- data_4 %>% dplyr::select(
  c(
    contains("wv"),
    contains("Conspir"),
    starts_with("trust"),
    starts_with('sci'),
    starts_with('acc_general_'),
    COVID_sev_general,
    COVID_pers_harm,
    COVID_pers_concern,
    COVID_concern4others,
    age,
    education,
    gender,
    COVID_govresponse_3,
    Gov_helpful,
    RKI_download,
    risk_of_harm_bt,
    proportionality_bt,
    data_security_bt,
    reduce_lik_bt,
    return_activ_fut,
    reduce_spread_fut,
    COVID_info_source_6,
    COVID_info_trust_6,
    COVID_info_source_2,
    COVID_info_trust_2
  )
) %>%
  dplyr::filter(gender < 3) %>%
  drop_na


# Sehr akzeptabel (1)	Einigermaßen akzeptabel (2) need to revscore

acceptability <-
  mod4_data %>% dplyr::select(starts_with('acc_general_'))
Acceptability <-
  revscore(acceptability, 4) %>% apply(., 1, mean, trim = .2, na.rm = TRUE)  


Libertarianism <-
  mod4_data %>% dplyr::select(c(wv_freemarket_best, wv_freemarket_lim, wv_lim_gov)) %>% mutate(wv_freemarket_lim_rev = revscore(wv_freemarket_lim, 7)) %>%
  dplyr::select(-wv_freemarket_lim) %>% apply(., 1, mean, na.rm = TRUE)  


COVIDrisk <-
  mod4_data %>% dplyr::select(c(
    COVID_sev_general,
    COVID_pers_harm,
    COVID_pers_concern,
    COVID_concern4others
  )) %>% apply(., 1, mean, na.rm = TRUE)  



Govguidelines_helpful <-
  mod4_data  %>% dplyr::select(Gov_helpful) %>% apply(., 1, mean, na.rm = TRUE)  

COVID_govresponse4 =  revscore(mod4_data$COVID_govresponse_3, 5) # 1 = extrem gut (reverse to 1 = gar nicht gut)
Germany_handling_thepandemic <-
 COVID_govresponse4


Conspiracism <- mod4_data  %>% dplyr::select(contains("Conspir")) %>%
  mutate(Conspir_6 = revscore(Conspir_6_rev, 5)) %>%
  dplyr::select(-Conspir_6_rev) %>%
  apply(., 1, mean, trim = .2, na.rm = TRUE)  


Scitech_positive <- mod4_data  %>% dplyr::select(starts_with('sci')) %>%
  apply(., 1, mean, na.rm = TRUE)  

# recode eductaion to group categories into none (4 --> 1), low(real (1) and haupt-schule (2) --> 2), medium (abitur=3), and high(uni=5 --> 4)

Education_recode = dplyr::recode(
  mod4_data$education,
  `4` = "low",
  `1` = "low",
  `2` = "low",
  `3` = "medium",
  `5` = "high",
  .default = NULL
)
Education <- factor(Education_recode, ordered = TRUE, levels = c("low", "medium", "high")) 



RKI_download = dplyr::recode(
  mod4_data$RKI_download,
  `1` = 1,
  `2` = 0,
  .default = NULL
)
CWA_download <- RKI_download

Trust_appsecurity <-
  mod4_data %>% dplyr::select(starts_with("trust"), data_security_bt) %>% apply(., 1, mean, na.rm =
                                                                           TRUE)  

CWA_effectiveness <-
  mod4_data %>% dplyr::select(reduce_lik_bt, return_activ_fut, reduce_spread_fut) %>% apply(., 1, mean, na.rm =
                                                                                       TRUE)  

Risk_of_harm <- mod4_data$risk_of_harm_bt


Socialmedia_source_and_trust <-
  mod4_data %>% dplyr::select(COVID_info_source_2, COVID_info_trust_2) %>% apply(., 1, mean, na.rm =
                                                                            TRUE)  

Govannouncements_source_and_trust <-
  mod4_data %>% dplyr::select(COVID_info_source_6, COVID_info_trust_6) %>% apply(., 1, mean, na.rm =
                                                                            TRUE)  

Gender_recode_male = dplyr::recode(mod4_data$gender,
                                   `1` = 1,
                                   `2` = 0,
                                   .default = NULL)
Gender_male <- Gender_recode_male

Age <- mod4_data$age


model_data4 <-
     as.data.frame(cbind(
      CWA_download,
      Acceptability,
      Libertarianism,
      Conspiracism,
      Scitech_positive,
      COVIDrisk,
      Govguidelines_helpful,
      Trust_appsecurity,
      Risk_of_harm,
     Education,
          Age,
      CWA_effectiveness,
      Germany_handling_thepandemic,
      Socialmedia_source_and_trust,
      Govannouncements_source_and_trust,
      Gender_male
    )) %>% mutate(Education = factor(Education, ordered = FALSE,  levels = c(2, 1, 3), labels = c("medium", "low", "high")) )
 
contrasts(model_data4$Education) <- contr.treatment(levels(model_data4$Education))








```



```{r, Correlation matrices}

corr_data3 <-
  model_data3 %>% ggcorr(
    label = TRUE,
    label_alpha = TRUE,
    method = c("pairwise", "pearson"),
    hjust = 1,
    layout.exp = 4
  ) +  theme_nice() +
  labs(title = "Correlation matrix: Wave 3")


corr_data4 <-
  model_data4 %>% ggcorr(
    label = TRUE,
    label_alpha = TRUE,
    hjust = 1,
    layout.exp = 4
  ) +  theme_nice() +
  labs(title = "Correlation matrix: Wave 4")



ggsave(
  filename = here("output/corr_plot3.pdf"),
  plot = corr_data3,
  dpi = 500,
  units = 'cm',
  height = 20,
  width = 30
)
ggsave(
  filename = here("output/corr_plot4.pdf"),
  plot = corr_data4,
  dpi = 500,
  units = 'cm',
  height = 20,
  width = 30
)



```

GLM (logistic regression): predictors for CWA download




```{r, logistic regression for CWA downloads}



glm3 <-
  glm(
    CWA_download ~  Trust_appsecurity + CWA_effectiveness + Acceptability +  Germany_handling_thepandemic + Govguidelines_helpful + Socialmedia_source_and_trust + Govannouncements_source_and_trust + Conspiracism + Libertarianism + COVIDrisk + Scitech_positive +  Gender_male + Age + Risk_of_harm + Education,
    data = model_data3,
    family = "binomial"
  )

#+ Education_high + Education_low + Education_medium
glm4 <-
  glm(
   CWA_download ~  Trust_appsecurity + CWA_effectiveness + Acceptability +  Germany_handling_thepandemic + Govguidelines_helpful + Socialmedia_source_and_trust + Govannouncements_source_and_trust + Conspiracism + Libertarianism + COVIDrisk + Scitech_positive +  Gender_male + Age + Risk_of_harm + Education,
    data = model_data4,
    family = "binomial"
  )


glm3_s <- arm::standardize(
    glm3,
    standardize.y = FALSE,
    binary.inputs = "center",
    unchanged = "Education"
    # unchanged = c("Education_high", "Education_low", "Education_medium")
)
display(glm3_s)

glm4_s <- arm::standardize(
    glm4,
    standardize.y = FALSE,
    binary.inputs = "center",
    unchanged = "Education"
    # unchanged = c("Education_low", "Education_medium", "Education_high")
    
)
display(glm4_s)




mr_plot <-
  plot_summs(
    glm3_s,
    glm4_s,
    colors = c("cornflowerblue", "#4cbc7c"),
    legend.title = "Wave",
    model.names = c("Wave 3", "Wave 4"),
    coefs = c(
      "Trust in CWA security" = "z.Trust_appsecurity",
      "Perception of CWA effectiveness" = "z.CWA_effectiveness",
      "Acceptance of privacy limits" = "z.Acceptability",
            "COVID-19 risk perception" = "z.COVIDrisk",
      "Belief in conspiracies" = "z.Conspiracism",
      "Social media use & trust" = "z.Socialmedia_source_and_trust",
      "Government announcements use & trust" =
        "z.Govannouncements_source_and_trust",
      "Approval of German pandemic response" =
        "z.Germany_handling_thepandemic",
      "Find government guidelines helpful" =
        "z.Govguidelines_helpful",
      "Attitudes to science and technology" = "z.Scitech_positive",
      "Libertarianism" = "z.Libertarianism",
      "CWA risk of harm perception" = "z.Risk_of_harm",
      "Age" = "z.Age",
      "Gender: male (vs. female)" = "c.Gender_male",
      "Education: low (vs. medium)" = "Educationlow",
      "Education: high  (vs. medium)" = "Educationhigh"
    )
  ) +
  # xlim(0, 2.5) +
  theme_nice() +
  labs(title = "Predictors of Corona-Warn-App (CWA) download")
mr_plot


ggsave(
  filename = here("output/mr_plot.pdf"),
  plot = mr_plot,
  dpi = 300,
  units = 'cm',
  height = 15,
  width = 26
)


stargazer(
  glm3_s,
  glm4_s,
  title = "Regression Results",
  align = TRUE,
  dep.var.labels = c("CWA downloads"),
  covariate.labels = c(
    "Trust in CWA security",
    "Perception of CWA effectiveness",
    "Acceptance of privacy limits",
    "Approval of German pandemic response",
    "Find government guidelenes helpful",
    "Social media use and trust",
    "Government announcements use and trust",
    "Belief in conspiracies",
    "Libertarianism",
    "COVID-19 risk perception",
    "Attitudes to science and technology",
    "Gender: male (vs. female)",
      "Age",
    "CWA risk of harm perception",
    "Education: low (vs. medium)",
    "Education: high  (vs. medium)"
  ),
  column.labels = c("Wave 3", "Wave 4"),
  ci = TRUE,
  ci.level = 0.95,
  no.space = TRUE,
  star.cutoffs = NA,
  omit.table.layout = "n"
)


```


GLM(lm): predictors for Trust_appsecurity

Combined measure for 3 items:

  1. How much do you trust the government to use the Corona-Warn-App data only to deal with the COVID-19 pandemic? 
  2. How much do you trust that the Corona-Warn-App is able to ensure the privacy of each individual that uses it?
  3. How secure is the data that is collected by the Corona-Warn-App?
 


```{r, linear models for trust in CWA security}

lm3 <-
  lm(
    Trust_appsecurity ~ Acceptability +  Germany_handling_thepandemic + Govguidelines_helpful + Socialmedia_source_and_trust + Govannouncements_source_and_trust + Conspiracism + Libertarianism + COVIDrisk + Scitech_positive + Risk_of_harm + Gender_male + Age + Education,
    data = model_data3
  )

lm4 <-
  lm(
    Trust_appsecurity ~  Acceptability +  Germany_handling_thepandemic + Govguidelines_helpful + Socialmedia_source_and_trust + Govannouncements_source_and_trust + Conspiracism + Libertarianism + COVIDrisk + Scitech_positive + Risk_of_harm + Gender_male + Age + Education,
    data = model_data4
  )

lm3_s <- standardize(
    lm3,
    unchanged = "Education",
    standardize.y = TRUE,
    binary.inputs = "center"
)
display(lm3_s)



lm4_s <- standardize(
    lm4,
    unchanged = "Education",
    standardize.y = TRUE,
    binary.inputs = "center"
)
display(lm4_s)

lm_34 <- plot_summs(
  lm3_s,
  lm4_s,
  scale = TRUE,
  model.names = c("Wave 3", "Wave 4"),
  legend.title = "",
  colors = c("cornflowerblue", "#4cbc7c"),
  coefs = c(
     "Acceptance of privacy limits" = "z.Acceptability",
            "COVID-19 risk perception" = "z.COVIDrisk",
      "Belief in conspiracies" = "z.Conspiracism",
      "Social media use & trust" = "z.Socialmedia_source_and_trust",
      "Government announcements use & trust" =
        "z.Govannouncements_source_and_trust",
      "Approval of German pandemic response" =
        "z.Germany_handling_thepandemic",
      "Find government guidelines helpful" =
        "z.Govguidelines_helpful",
      "Attitudes to science and technology" = "z.Scitech_positive",
      "Libertarianism" = "z.Libertarianism",
      "CWA risk of harm perception" = "z.Risk_of_harm",
            "Gender: male (vs. female)" = "c.Gender_male",
     "Age" = "z.Age",
      "Education: low (vs. medium)" = "Educationlow",
      "Education: high  (vs. medium)" = "Educationhigh"
  )
) +
  # xlim(-0.5, 0.5) +
  theme_nice() +
  labs(subtitle = "Predictors of Trust in Corona-Warn-App (CWA) Security")
lm_34


stargazer(
  lm3_s,
  lm4_s,
  title = "Regression Results for Figure ",
  align = TRUE,
  dep.var.labels = c("Trust in the CWA security"),
  covariate.labels = c(
    "Acceptance of privacy limits",
    "Approval of German pandemic response",
    "Find government guidelines helpful",
    "Social media use and trust",
    "Government announcements use and trust",
    "Belief in conspiracies",
    "Libertarianism",
    "COVID-19 risk perception",
    "Attitudes to science and tech",
     "CWA risk of harm perception",
    "Gender: male (vs. female)",
      "Age",   
    "Education: low (vs. medium)",
    "Education: high  (vs. medium)"
  ),
  column.labels = c("wave3", "wave4"),
  ci = TRUE,
  ci.level = 0.95,
  no.space = TRUE,
  star.cutoffs = NA,
  omit.table.layout = "n"
)

ggsave(
  filename = here("output/lm_34_arm.pdf"),
  plot = lm_34,
  dpi = 300,
  units = 'cm',
  height = 15,
  width = 26
)

```



```{r, linear models for CWA effectiveness}

lm3eff <-
  lm(
    CWA_effectiveness ~ Acceptability +  Germany_handling_thepandemic + Govguidelines_helpful + Socialmedia_source_and_trust + Govannouncements_source_and_trust + Conspiracism + Libertarianism + COVIDrisk + Scitech_positive + Risk_of_harm + Gender_male + Age + Education,
    data = model_data3
  )

lm4eff <-
  lm(
    CWA_effectiveness ~  Acceptability +  Germany_handling_thepandemic + Govguidelines_helpful + Socialmedia_source_and_trust + Govannouncements_source_and_trust + Conspiracism + Libertarianism + COVIDrisk + Scitech_positive + Risk_of_harm + Gender_male + Age + Education,
    data = model_data4
  )

lm3eff_s <- standardize(
    lm3eff,
    unchanged = "Education",
    standardize.y = TRUE,
    binary.inputs = "center"
)
display(lm3eff_s)

lm4eff_s <- standardize(
    lm4eff,
    unchanged = "Education",
    standardize.y = TRUE,
    binary.inputs = "center"
)
display(lm4eff_s)

lm_34eff <- plot_summs(
  lm3eff_s,
  lm4eff_s,
  scale = TRUE,
  model.names = c("Wave 3", "Wave 4"),
  legend.title = "Wave",
  colors = c("cornflowerblue", "#4cbc7c"),
  coefs = c(
    "Acceptance of privacy limits" = "z.Acceptability",
    "COVID19 risk perception" = "z.COVIDrisk",
    "Belief in conspiracies" = "z.Conspiracism",
    "Social media use & trust" = "z.Socialmedia_source_and_trust",
    "Government announcements use & trust" =
      "z.Govannouncements_source_and_trust",
    "Approval of German pandemic response" =
      "z.Germany_handling_thepandemic",
    "Find government guidelines helpful" =
      "z.Govguidelines_helpful",
    "Attitudes to science and technology" = "z.Scitech_positive",
    "Libertarianism" = "z.Libertarianism",
    "CWA risk of harm perception" = "z.Risk_of_harm",
    "Gender: male (vs. female)" = "c.Gender_male",
    "Age" = "z.Age",
    "Education: low (vs. medium)" = "Educationlow",
    "Education: high  (vs. medium)" = "Educationhigh"
  )
) +
  # xlim(-0.5, 0.5) +
  theme_nice() +
  labs(subtitle = "Predictors of perceived effectiveness of Corona-Warn-App (CWA)")

lm_34eff

stargazer(
  lm3eff_s,
  lm4eff_s,
  title = "Regression Results for Figure ",
  align = TRUE,
  dep.var.labels = c("Perceived effectiveness of the CWA"),
  covariate.labels = c(
    "Acceptance of privacy limits",
    "Approval of German pandemic response",
    "Find governement guidelenes helpful",
    "Social media use and trust",
    "Governement announcements use and trust",
    "Belief in conspiracies",
    "Libertarianism",
    "Covid-19 risk perception",
    "Attitudes to science and tech",
    "CWA risk of harm perception",
    "Gender: male (vs. female)",
    "Age",
    "Education: low (vs. medium)",
    "Education: high  (vs. medium)"
  ),
  column.labels = c("Wave 3", "Wave 4"),
  ci = TRUE,
  ci.level = 0.95,
  no.space = TRUE,
  star.cutoffs = NA,
  omit.table.layout = "n"
)


ggsave(
  filename = here("output/lm_34eff_arm.pdf"),
  plot = lm_34eff,
  dpi = 300,
  units = 'cm',
  height = 15,
  width = 26
)

```



```
